---
title: "DOse-response modeling using ModStan"
author: "Burak Kürsad Günhan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{Fitting Binomial-Normal hierarchical model using MetaStan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
fig_caption: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Introduction
Dose-response modeling in drug finding trials is an important part of the drug development. We introduced the shrinkage estimation to estimate dose-response fucntion in phase II trials with multiple subgroups, for instanse dose regimens. To automate the implementation, we developed `ModStan` which uses **Stan** (a modern MCMC engine) to fit several models including pooling, shrinkage and stratified analysis. This package is the accompanying package of @Guenhan. See @Guenhan for model descriptions.


## Installation 
The development version of `ModStan` is available on Github ([https://github.com/gunhanb/ModStan](https://github.com/gunhanb/ModStan)) and can be installed using `devtools` package as follows:

```{r install, eval = FALSE}
devtools:::install_github("gunhanb/ModStan")
```

The dupilumab example is available in the package, and it can be loaded as follows:

```{r dataset}
library("ModStan")
data("dat.Dupilumab", package = "ModStan")
head(dat.Dupilumab)
```

Additional information can be obtained by typing `?dat.Dupilumab` (for any dataset and function in the package). 

## Fitting a binomial-normal hierarchical model
`mod_stan` is the main fitting function of this package. The main computations are executed via the `rstan` package's `sampling` function. We can fit the binomial-normal hierarchical model [@Guenhan] using a weakly informative prior for treatment effect as follows:


```{r bnhmFit, results="hide"}
shrinkage.Dupilumab.stan  <- mod_stan(dose = dose,
                                      resp = resp,
                                      subgroup = subgroup,
                                      frequency = frequency,
                                      data = dat.Dupilumab,
                                      model = "Shrinkage",
                                      beta_prior =  1,
                                      beta_prior_dist = "half-normal")
```


Convergence diagnostics, very conveniently, obtained using `shinystan` package as follows:

```{r shinystan, eval = FALSE}
library("shinystan")
## Firstly convert "stan" object to a "shinystan" object
launch_shinystan(shrinkage.Dupilumab.stan$fit_sum)
```

A simple summary of the fitted model is given by `print` option:

```{r print}
print(shrinkage.Dupilumab.stan)
```


Please see @Guenhan and @Feller for complete model descriptions.


# References
