---
title: "Dose-response modeling using ModStan"
author: "Burak Kürsad Günhan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dose-response modeling of phase II trials with multiple schedules using ModStan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
fig_caption: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
```

## Introduction
Dose-response modeling in drug finding trials is an important part of the drug development. We introduced the spartial pooling with schedule specific random effects for the $ED_{50}$ parameter to estimate dose-response fucntion in phase II trials with multiple schedules (dose regimens). To automate the implementation, we developed `ModStan` which uses **Stan** (a modern MCMC engine) to fit several models including pooling, shrinkage and stratified analysis. This package is the accompanying package of Günhan, Meyvisch, and Friede (2020).


## Installation 
The development version of `ModStan` is available on Github ([https://github.com/gunhanb/ModStan](https://github.com/gunhanb/ModStan)) and can be installed using `devtools` package as follows:

```{r install, eval = FALSE}
devtools:::install_github("gunhanb/ModStan")
```

The dupilumab example is available in the package, and it can be loaded as follows:

```{r dataset}
library("ModStan")
data("dat.Dupilumab", package = "ModStan")
head(dat.Dupilumab)
```

Additional information can be obtained by typing `?dat.Dupilumab` (for any dataset and function in the package). 

## Fitting a partial pooling with random effects (PP - RE) model
`mod_stan` is the main fitting function of this package. The main computations are executed via the `rstan` package's `sampling` function. We can fit the partial pooling with random effects (PP - RE) model (Günhan, Meyvisch, and Friede, 2020) using a weakly informative prior for heterogeneity paarmeter as follows:


```{r PPREfit, results="hide"}
PPRE.Dupilumab.stan  <- mod_stan(dose = dose,
                                 resp = resp,
                                 schedule = schedule,
                                 sigma = sigma,
                                 freq = freq,
                                 freq_ref = 24 * 7 * 2,
                                 data = dat.Dupilumab,
                                 model = "PP-RE",
                                 stan_seed = 2234,
                                 tau_prior =  1,
                                 tau_prior_dist = "half-normal")
```


Convergence diagnostics, very conveniently, obtained using `shinystan` package as follows:

```{r shinystan, eval = FALSE}
library("shinystan")
## Firstly convert "stan" object to a "shinystan" object
launch_shinystan(PPRE.Dupilumab.stan$fit_sum)
```

A simple summary of the fitted model is given by `print` option:

```{r print}
print(PPRE.Dupilumab.stan)
```


Please see Günhan, Meyvisch, and Friede (2020) and Feller et al (2017) for complete model descriptions.


# References

Feller, C., Schorning, K., Dette, H., Bermann, G., and Bornkamp, B. (2017). Optimal designs for
dose response curves with common parameters. Annals of Statistics, 45(5):2102–2132.

Günhan, B.K., Meyvisch, P., and Friede, T. (2020). Shrinkage estimation for dose-response modeling in phase II trials
with multiple schedules. In preparation. 
